{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
Starting creating tables

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(t)
	\end{equation}

@@

	\begin{equation}
		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
	\end{equation}

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

@@

	{\color{red} We have to clean this up theoretically. Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.}

	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s) \phi_j(s)\right] \right] \mathrm{d}s + \epsilon(\omega) \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
		\end{split}
	\end{equation}

	Using sample analogues, we can use this form to obtain the following approximation.

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \hat{\xi}^m(\omega) \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
	\end{equation}

	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.

	\begin{equation}
		y_i \approx \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{L} \left[b_j \sum_{m  = 1}^{M}  \tilde{\xi}^{m,L}_{i} \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
	\end{equation}

@@

	\begin{figure}[H]\label{bspline_basis}
		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
	\end{figure}

>>>>

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
	\end{equation}

@@

	\begin{equation}
		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
	\end{equation}

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

@@

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice

@@

	\begin{figure}[H]\label{bspline_basis}
		\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
		\caption{B-spline basis functions of order 3 for 6 equidistant knots on $[0,1]$}
	\end{figure}
\newpage
	\subsection{Simulation Study Results}

	\begin{table}[htb]
			\centering
			\caption{Monomial Basis Expansion Regression}
				\begin{tabular}{lllllll}
					\cline{1-5}
					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
7.177234352026647                        & 131.92716520680838                        & 0.8936725847175324                         & 2.5839516380614462                        & 2       &  \\
4.170391190343292                        & {\color[HTML]{FE0000} 129.64258934345224} & 0.8122408608804015                         & 2.511772278865247                         & 3       &  \\
3.912749103345826                        & 130.1170783435205                         & 0.3807927171910713                         & 2.090474762002978                         & 4       &  \\
{\color[HTML]{FE0000} 3.638501968909747} & 130.59817144950233                        & {\color[HTML]{FE0000} 0.09216751463887264} & {\color[HTML]{FE0000} 1.8134256416939782} & 5       &  \\
6.016442343989896                        & 201.15534584991525                        & 0.7620805051836907                         & 3.3937342332820926                        & 6       & 
\end{tabular}
\end{table}

\vspace{2cm}

	\begin{table}[htb]
			\centering
			\caption{BSpline Basis Expansion Regression}
				\begin{tabular}{lllllll}
					\cline{1-5}
					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
3.9127490963955247                        & {\color[HTML]{FE0000} 130.1170783090359} & 0.3807927168700936                          & 2.090474761101881                         & 4       &  \\
{\color[HTML]{FE0000} 3.6430480624640396} & 130.61094959896604                       & 0.09511820431115069                         & 1.8164314387816713                        & 5       &  \\
3.6542611008674575                        & 131.35354539843397                       & 0.07775281510299467                         & {\color[HTML]{FE0000} 1.8091346529425483} & 6       &  \\
3.6770545937377634                        & 132.14205183557064                       & 0.07518488287219192                         & 1.8168036577708813                        & 7       &  \\
3.710740869697218                         & 133.3653658811635                        & 0.05810108378740701                         & 1.8164984632128844                        & 8       &  \\
3.7192146351418724                        & 133.6814928169343                        & 0.05640282340664383                         & 1.8193083539013821                        & 9       &  \\
3.742010447810594                         & 134.5121710907784                        & 0.0521785231194299                          & 1.8257576297312081                        & 10      &  \\
3.7643964092462974                        & 135.29727347111702                       & {\color[HTML]{FE0000} 0.051902252769905684} & 1.8360966075573522                        & 11      &  \\
3.80109308638683                          & 136.5758146586355                        & 0.052040315671138586                        & 1.8531479959118535                        & 12      &  \\
3.834360204971099                         & 137.78406681481994                       & 0.052706573106132304                        & 1.869969847032031                         & 13      &  \\
3.862166917165765                         & 138.73431326927349                       & 0.053068654178390816                        & 1.8826933364948355                        & 14      &  \\
3.8685638723557956                        & 138.97427074660192                       & 0.0525955164519272                          & 1.8848221385552892                        & 15      &  \\
3.88505750612787                          & 139.57418873526626                       & 0.05283448721173191                         & 1.8933474257957223                        & 16      &  \\
3.912671952971778                         & 140.51490301138338                       & 0.053220205231306356                        & 1.9061942087104604                        & 17      &  \\
3.948125713522542                         & 141.80885020010606                       & 0.053584434348457485                        & 1.9231184762987383                        & 18      & 
\end{tabular}
\end{table}

\vspace{2cm}

	\begin{table}[htb]
			\centering
			\caption{Fourier Basis Expansion Regression}
				\begin{tabular}{lllllll}
					\cline{1-5}
					 \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{1-5}
3.6975216821108177                        & {\color[HTML]{FE0000} 129.19133735032568} & 0.6952364931614831                         & 2.394399533437222                         & 3       \\
{\color[HTML]{FE0000} 3.6347035142043147} & 130.59281554182246                        & 0.07418129892625985                        & 1.795816800944426                         & 5       \\
3.6762259845089287                        & 132.0824820138016                         & 0.05147130962678385                        & {\color[HTML]{FE0000} 1.7934269021325526} & 7       \\
3.718852537544315                         & 133.67575428625497                        & {\color[HTML]{FE0000} 0.05104970622270979} & 1.812908100982769                         & 9       \\
3.764506721475903                         & 135.26218648523314                        & 0.05146451789575423                        & 1.8346302450265894                        & 11      \\
3.810949927900835                         & 136.90281800923086                        & 0.05197380387819929                        & 1.8572425102431276                        & 13      \\
3.8567441840723165                        & 138.57257529224665                        & 0.05252120988973837                        & 1.8802107534919845                        & 15      \\
3.9061852571557436                        & 140.29178124765565                        & 0.05304327165297495                        & 1.9028253007284568                        & 17      \\
3.9551703628111876                        & 142.057266882177                          & 0.053647142499864804                       & 1.9271845824346567                        & 19     
\end{tabular}
\end{table}
